Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-07-19 results/tables/table_1.Rmd
Update references and add to Table 1

make_study_label <- function(dataset){
	study <- ifelse(dataset=="hmp", "HMP", capwords(dataset))
}

@@

@@

	list(study = capwords(study),
				n_subjects = as.character(n_subjects),
				per_obese = per_obese,
				bmi_summary = bmi,
				per_female = per_female,
				age_summary = age,
				per_white = per_white,
				method = technology[study],
				region = region[study],
				beta_p = format_p(beta_summary[study,'p_value']))
}

@@

#colnames(study_summary) <- LETTERS[1:8]
colnames(study_summary) <- c("Study", "\\bigcell{c}{Subjects \\\\ (N)}",
													"\\bigcell{c}{Obese \\\\ (\\%)}",
													"\\bigcell{c}{Average BMI \\\\ (Min-Max)}",
													"\\bigcell{c}{Female \\\\ (\\%)}",
													"\\bigcell{c}{Average Age \\\\ (Min-Max)}",
													"\\bigcell{c}{Non-Hispanic \\\\ White (\\%)}",
													"\\bigcell{c}{Sequencing \\\\ Method}",
													"\\bigcell{c}{16S rRNA \\\\ Gene Region}",
													"\\bigcell{c}{AMOVA \\\\ (P-value)}")

>>>>

make_study_label <- function(dataset){
	study <- ifelse(dataset=="hmp", "HMP", capwords(dataset))
	paste0(study, " (", citation[dataset], ")")
}

@@

citation <-  c(
	baxter = "23",#
	escobar = "16",#
	hmp = "21",#
	ross = "18",#
	schubert = "22",#
	turnbaugh = "6",#
	wu = "20",#
	zupancic = "15",#
	goodrich = "19",#
	zeevi = "17"#
)

@@

	list(study = make_study_label(study),
				n_subjects = as.character(n_subjects),
				per_obese = per_obese,
				bmi_summary = bmi,
				per_female = per_female,
				age_summary = age,
				per_white = per_white,
				method = technology[study],
				region = region[study],
				beta_p = format_p(beta_summary[study,'p_value']))
}

@@

#colnames(study_summary) <- LETTERS[1:8]
colnames(study_summary) <- c("Study (Ref.)", "\\bigcell{c}{Subjects \\\\ (N)}",
													"\\bigcell{c}{Obese \\\\ (\\%)}",
													"\\bigcell{c}{Average BMI \\\\ (Min-Max)}",
													"\\bigcell{c}{Female \\\\ (\\%)}",
													"\\bigcell{c}{Average Age \\\\ (Min-Max)}",
													"\\bigcell{c}{Non-Hispanic \\\\ White (\\%)}",
													"\\bigcell{c}{Sequencing \\\\ Method}",
													"\\bigcell{c}{16S rRNA \\\\ Gene Region}",
													"\\bigcell{c}{AMOVA \\\\ (P-value)}")
